Modeling Time-Variable Elemental Abundances in Coronal Loop Simulations

### 2024-05-09 src/tex/ms.tex
[showyourwork] overleaf sync

% Define document class
\documentclass[twocolumn,tighten,linenumbers]{aastex631}
\usepackage{showyourwork}
\usepackage{subfigure}  
\usepackage{amsmath}
\usepackage{hyperref}

@@

We use the \texttt{ebtel++} code\footnote{https://github.com/rice-solar-physics/ebtelPlusPlus} \citep{barnes2016} to model the hydrodynamics and the effects of time-variable elemental abundances in a coronal loop.  The code solves the zero-dimensional (coronally-averaged) hydrodynamics equations as a function of time for a coronal loop \citep{klimchuk2008,cargill2012a,cargill2012b}.  Because of the code's extreme speed, it can run parameter surveys within seconds, and generally compares well with higher dimensional models \citep{barnes2016}.  This makes it a powerful tool to understand the importance of several physical effects in various regimes.

@@

\nopagebreak

\leavevmode \newline

>>>>

% Define document class
\documentclass[twocolumn,tighten,linenumbers]{aastex631}
\usepackage{showyourwork}
\usepackage{subfigure}  
\usepackage{amsmath}
\usepackage{hyperref}
\usepackage{microtype}

@@

We use the \texttt{ebtel++} code\footnote{\url{https://github.com/rice-solar-physics/ebtelPlusPlus}} \citep{barnes2016} to model the hydrodynamics and the effects of time-variable elemental abundances in a coronal loop.  The code solves the zero-dimensional (coronally-averaged) hydrodynamics equations as a function of time for a coronal loop \citep{klimchuk2008,cargill2012a,cargill2012b}.  Because of the code's extreme speed, it can run parameter surveys within seconds, and generally compares well with higher dimensional models \citep{barnes2016}.  This makes it a powerful tool to understand the importance of several physical effects in various regimes.

@@
